A neural coarse graining theory of consciousness

### 2018-07-02 Paper_neural_coarse_graining_of_consciousness.tex
Save before branching

			%% our claim 
				@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.

@@

		\subsection{reflexive behaviours is unconscious (or environment-state dependent processes)}\label{sec:reflexive}
			\subsubsection{Reflection}
				\begin{ants}
					@ Reflexive systems is not informational closured. 
					@ Based on our theory, 
					@ x -> s -> a
						@@ the system state is determined by environmental state, then it is not conscious. 
					@ Therefore, in general, a simple policy network is not conscious. 
				\end{ants}

@@

	\section{About Phenomenology (conscious processing)}
		\subsection{Perceptual overflow}
		\subsection{Planning}
		\subsection{Imagination}
		\subsection{Dream vs non-dream sleep}
		\subsection{Binocular rivalry}
		\subsection{Hallucinations}
		\subsection{Synaesthesia}

@@

			\begin{comment}

@@

@@

		\subsection{Predictive Brain}

			* Because of this XXXX, the representation has the maximal \ac{ntic} also has the maximal predictive power of the external environment. \todo[inline]{I need math here!!}

			* Therefore, it's reasonably assume that if evolution wants to build predictive mechanisms, the mechanisms should be settled on the information at the \ac{cged} level.

			* More specifically, a forward model, which received state and action as input and compute transition and then output next states, should be build on the representation that forms the \acl{ic}.

			* Therefore, the state of predictive model can be conscious while it is linked to \acl{ic} representation.

			* Note that, a system showing some predictive power is not sufficient to be conscious.

			* For example, the proportional–integral–derivative controller (PID) controller shows predictive behaviours due to its derivative which computes and predict error value in the future. Derivative action predicts system behaviour and thus improves settling time and stability of the system.

			* However, the state of the whole PID system still be determined by the inputs, i.e. the states of the controlled process, thus cannot complete \acl{ic}.

@@

			* Similarly, the neural system also has many circuits that show predictive power but do not have \ac{ic}.

@@

		\subsection{About location of NTIC}
		\subsection{Attention}
%		\subsection{We didn't specify what dynamic in the NTIC process associates with conscious contents.}
		\subsection{Finding coarse-grain function}
			\begin{ants}
				@ It's not clear what the coarse-graining function is.\todo[color=red]{this should be explained by environmental deterministic}

>>>>

			%% our claim 
				@

				@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.

@@

		\subsection{reflexive behaviours is unconscious (or environment-state dependent processes)}\label{sec:reflexive}
			\subsubsection{Reflection}
				\begin{ants}
					@ Reflexive systems is not informational closured. 
					@ Base	d on our theory, 
					@ x -> s -> a
						@@ the system state is determined by environmental state, then it is not conscious. 
					@ Therefore, in general, a simple policy network is not conscious. 
				\end{ants}

@@

	\section{About Phenomenology (conscious processing)}
		\subsection{Perceptual overflow}
		\subsection{Volition and freewill}
			\begin{ants}
				@ Volition is a result of coarse-graining

				@ Lebel's experiment can be well explained by the experiment.
			\end{ants}

		\subsection{Planning}
		\subsection{Imagination}
		\subsection{Dream vs non-dream sleep}
		\subsection{Binocular rivalry}
		\subsection{Hallucinations}
		\subsection{Synaesthesia}

@@

			\begin{comment} % materials

@@

				@ \rewrite{According to Noë, perceptual presence is explained by a “ sensorimotor theory ” on which perception depends on a practical mastery of sensorimotor dependencies or “ sensorimotor contingencies ” (SMCs) (O ’ Regan & Noë, 2001). The theory inherits from Gibsonian notions of “ affordances ” (Gibson, 1979) and from enactive cognitive science (Thompson & Varela, 2001) which stress the importance of brain-body-world interactions in cognitive processes. On sensorimotor theory, the perception of a tomato as a (perceptually present, real, subjectively veridical) tomato is given by practical mastery of the SMCs governing how the sensory responses elicited by the tomato will behave in a variety of situations. A strong point of this theory is that it suggests why there are differences in qualitative character between modalities, the reason being that different modalities instantiate different SMCs (O ’ Regan & Noë, 2001). }

@@

		\subsection{Predictive Processing}				
			\begin{ants}
				%% Introduce PP
				@ The predictive processing is a powerful framework (PP) which integrates several influential ideas in the history of neuroscience including "perception as unconscious inference" from Helmholtz \citet{helmholtz1866concerning}, "analysis by synthesis", “predictive coding”, "Bayesian brain hypothesis"

				@ is a powerful framework

				@ a recent emerged theoretical framework of perception and brain function, which suggests that the brain continuously generates and updates predictions about incoming sensory signals, represents a general principle of neural functioning.

				@ According to predictive processing (PP) account of perception, the neural system constantly performs unconscious statistical inference about hidden causes in the external environment. The perceptual contents are the "best guess" about the environment 	\cite{clark_2013}			\cite{Hohwy2013}

				@ Bperceptual content is the result of probabilistic inference on the hidden causes of sensory signals.

				@ Because it is well integrated with Bayesian brain hypothesis, the PP framework has been used to interpret conscious perception in many perceptual domain. \cite{Hohwy2013} \cite{SethPP2014}

				%% The gaps between pp and consciousness
				@ However, to link PP to consciousness, there are still two major gaps.

					@@ First, previous studies have demonstrated many brain processes following the principle of Bayesian inference and Bayesian integration. But not all these processes are conscious. This indicates that PP is not a sufficient mechanism for conscious perception. Some other factors may be involved to determine which PPs can be conscious or not.

					@@ Second, it has been emphasized that only the results of the inference or prediction can be consciously accessed. The process of inference in completely unconscious. So WHY?

				@ Even though PP has been acquiring attention in different discipline in neuroscience, So far, to our knowledge, no detailed explanation has been given to account for the two questions.

				% 2018/06/15 15:10
				@ We first hypothesize that predictive processing stays unconscious is because it is not able to achieve NTIC.

					@@ \toWrite{Example from PID controller}

				@ Second, according to our theory, it is obvious that the computation of predictive processing is unconscious and only the result is conscious. Because the computational details is not at the coarse-grained level which achieves NTIC.

					@@ So far, many neuronal models and coding schema have been proposed to explain how to implement Bayesian inference and prediction at the neuronal level.

					@@ However?

				@ We hypothesize that the distinction between conscious and unconscious predictive mechanisms is whether they build up on the information from the NTIC process.

			\begin{writingMaterials}

				%% About the unconscious Bayesian processing
				@ \cite{lamme2015predictive}
					@@ To my knowledge, this is the first time this has been so explicitly laid out—writers on predictive coding thus far have always stayed a little vague on where exactly consciousness sits in the Bayesian framework.

					@@ Yet the two points seem contradictory. In the Bayesian predictive coding framework, consciousness is the result of the unconscious inferential processes.

					@@ However, these authors have so far been very reticent about how exactly consciousness ﬁts into the PC framework. For now, there is an emerging idea that understands consciousness as the ﬁnal result of unconsciousness processing. According to Hohwy (2013), perceptual consciousness ﬁts in the PC theory as the ‘upshot’ or ‘conclusion’ of unconscious perceptual inferences. Melloni (2014) also expects that inferential processes are conducted behind the curtain of consciousness and what we experience are the ‘outcomes’ or ‘results’ of an unconsciou inferential process. Lamme (2015) agrees with the idea that consciousness is based on the relation or more precisely conjunction of current inputs and priors, which together produce posterior beliefs. Karl Friston agrees to a certain extent with this interpretation of consciousness. According to Hobson and Friston (2016), consciousness is not a phenomenon but a process, a process of optimizing beliefs through inference (consciousness, dreams, and inference; the Cartesian theater revisited; a response to our theater critics).

				@ Link PP and c
					@@ \cite{hobson2016response}
					@@ \cite{Melloni2015}

				%% ----------------------------------------------------------------------------
				@ \cite{SethPP2014}

				@ When uncertainty is high, we should expect an increase in the ability of ever higher-level prior beliefs to determine conscious experience. I

				@ determine conscious experience.

				@ PP combines and builds upon previous ideas about the role of “unconscious inference” in perception (Helmholtz, 1925; Barlow, 1961; Gregory, 1970), the process of “analysis by synthesis” in psychology (Neisser, 1967), the “predictive coding” approach in neuroscience (Srinivasan et al., 1982; Rao and Ballard, 1999; Huang and Rao, 2011) and “generative models” and related probabilistic computational principles (MacKay, 1956; Mumford, 1992; Dayan et al., 1995; Hinton, 2007a,b; Tenenbaum et al., 2011).

				@ \rewrite{The brain is constantly confronted with a wealth of sensory information that must be processed efficiently to facilitate appropriate reactions. One way of optimizing this processing effort is to predict incoming sensory information based on previous experience so that expected information is processed efficiently and resources can be allocated to novel or surprising information. Theoretical and computational studies led to the formulation of the predictive coding framework (Friston 2005, Hawkins and Blakeslee 2004, Mumford 1992, Rao and Ballard 1999). Predictive coding states that the brain continually generates models of the world based on context and information from memory to predict sensory input. In terms of brain processing, a predictive model is created in higher cortical areas and communicated through feedback connections to lower sensory areas. In contrast, feedforward connections process and project an error signal, i.e. the mismatch between the predicted information and the actual sensory input (Rao \& Ballard, 1999). The predictive model is constantly updated according to this error signal. }

				@ \rewrite{Predictive inference and perception The concept of PC overturns classical notions of perception as a largely ‘bottom-up’ process of evidence accumulation or feature detection, proposing instead that perceptual content is speciﬁed by top-down predictive signals that emerge from hierarchically organized generative models of the causes of sensory signals. According to PC, the brain is continuously attempting to minimize the discrepancy or ‘prediction error’ between its inputs and its emerging models of the causes of these inputs via neural computations approximating Bayesian inference (Figure 1 and Box 1). Importantly, prediction errors can be minimized either by updating generative models (perceptual inference and learning; changing the model to ﬁt the world) or by performing actions to bring about sensory states in line with predictions (active inference; changing the world to ﬁt the model).}

				@ \rewrite{In terms of brain function, Hermann von Helmholtz’s 19th Century notion of perception as unconscious inference has found new momentum in modern formulations of ‘predictive processing’, the Bayesian brain, and the ‘free energy principle’ (Clark, 2013; Friston, 2010; Hohwy, 2013). On these formulations, which can all be subsumed under the general term ‘prediction error minimization’ (PEM, (Hohwy, 2013)) perceptual content is the result of probabilistic inference on the hidden causes of sensory signals. }

				@ \rewrite{Generative models encoded by brain structure and dynamics make predictions about sensory inputs, based on prior expectations. Action (e.g., body movements) and perception conspire to reduce sensory prediction errors, giving rise to perceptual content and}

				@ \rewrite{More informally, what we perceive is the brain’s ‘best guess’ of what’s out there (or ‘in here’, for perceptions of body and self).}

				@ \rewrite{“ predictive processing ” (PP) 1 or the “ Bayesian brain ” this holds that perceptual content is determined by hierarchically organized generative (i.e., predictive) models (HGMs) of the external causes of sensory signals, induced by a process approximating Bayesian inference (Friston, 2009).}

				@ Not all predictive mechanism are conscious.

				@ We hypothesize that the distinction between conscious and unconscious predictive mechanisms is whether they build up on the information from the NTIC process.

				@ we can also explain why only the result (posterior) of predictive processing is conscious.

				@ Because of this XXXX, the representation has the maximal \ac{ntic} also has the maximal predictive power of the external environment. \todo[inline]{I need math here!!}

				@ Therefore, it's reasonably assume that if evolution wants to build predictive mechanisms, the mechanisms should be settled on the information at the \ac{cged} level.

				@ More specifically, a forward model, which received state and action as input and compute transition and then output next states, should be build on the representation that forms the \acl{ic}.

				@ Therefore, the state of predictive model can be conscious while it is linked to \acl{ic} representation.

				@ Note that, a system showing some predictive power is not sufficient to be conscious.

				@ For example, the proportional–integral–derivative controller (PID) controller shows predictive behaviours due to its derivative which computes and predict error value in the future. Derivative action predicts system behaviour and thus improves settling time and stability of the system.

				@ However, the state of the whole PID system still be determined by the inputs, i.e. the states of the controlled process, thus cannot complete \acl{ic}.

@@

				@ Similarly, the neural system also has many circuits that show predictive power but do not have \ac{ic}.

@@

		\subsection{About location of NTIC}
		\subsection{Attention}
			Attention can be when the neural want to output a specific information in NTIC.

%		\subsection{We didn't specify what dynamic in the NTIC process associates with conscious contents.}

		\subsection{Finding coarse-grain function}
			\begin{ants}
				@ It's not clear what the coarse-graining function is.\todo[color=red]{this should be explained by environmental deterministic}
